%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Software Engineer} % Job title
{LLC The Invaders} % Organization
{Novosibirsk, Russia} % Location
{Oct. 2014 - PRESENT} % Date(s)
{
Responsibilities: Development of android applications using Java and Kotlin; Development server side REST API for different clients using Python, Django, Java, Kotlin, Vert.x; Configuration servers and development auto deployment scripts.\linebreak
\linebreak
Projects in which I participated:\linebreak
\linebreak
\begin{cvitems}
    \item {
        \begin{flushleft}
            "Money Zebra MVP" --- Online auction (Still in development). (Kotlin with Vert.x, TypeScript with Angular, Python with Django)\linebreak
            Responsibilities: Full stack.\linebreak
            Auction: \url{https://au.zebra.money/}\linebreak
            Web site: \url{http://zebra.money/}\linebreak
        \end{flushleft}
    }
    \item {
        \begin{flushleft}
            RecyclerOS MVP - Microservice for encryption documents and store it to ethereum blockchain — It is a global solution for the problems of the recycling industry. (Kotlin with Vert.x)\linebreak
            Web site: \url{https://troventum.com/}\linebreak
        \end{flushleft}
    }
    \item {
        \begin{flushleft}
            Android client for RecyclerOS MVP — It is a global solution for the problems of the recycling industry. (Kotlin)\linebreak
            Web site: \url{https://troventum.com/}\linebreak
        \end{flushleft}
    }
    \item {
        \begin{flushleft}
            Android application "Staffjet" --- Staffjet is HRaas-service for mass selection and hiring of personnel for non-specialized positions. (Kotlin)\linebreak
            Web site: \url{https://staffjet.ru/}\linebreak
            Googleplay: \url{https://play.google.com/store/apps/details?id=ru.staffjet}\linebreak
        \end{flushleft}
    }
    \item {
        \begin{flushleft}
            Android application "Humaniq Lite" --- Humaniq is a simple and secure mobile bank. (Java)\linebreak
            Responsibilities: Chat core implementation.\linebreak
            Web site: \url{http://humaniq.com/}\linebreak
            Googleplay: \url{https://play.google.com/store/apps/details?id=com.humaniq.lite}\linebreak
            Source code: \url{https://github.com/humaniq/humaniq-android-lite}\linebreak
        \end{flushleft}
    }
    \item {
        \begin{flushleft}
            Android application "Humaniq Prototype" --- Humaniq is a simple and secure mobile bank. (Java)\linebreak
            Source code: \url{https://github.com/humaniq/humaniq-android}\linebreak
        \end{flushleft}
    }
    \item {
        \begin{flushleft}
            Server side for "Humaniq Prototype" ---
            Serever side for application as bankink functionality here using own crypthographic currency called "HMQ" implemented on Ethereum smart contracts (Django with Python)\linebreak
            Source code: \url{https://github.com/humaniq/humaniq-django-server}\linebreak
        \end{flushleft}
    }
    \item {
        \begin{flushleft}
            Implemented android application "Starateli" --- construction materials catalog. (Java)\linebreak
            Googleplay: \url{https://play.google.com/store/apps/details?id=ru.starateli}\linebreak
        \end{flushleft}
    }
\end{cvitems}
}

\cventry
{} % Job title
{} % Organization
{} % Location
{} % Date(s)
{
\begin{cvitems}
    \item {
        \begin{flushleft}
            Android application "Revengebet" --- Sport forecasts. (Java)\linebreak
            Googleplay: \url{https://play.google.com/store/apps/details?id=com.revengebet_limited}\linebreak
            Aptoide: \url{https://revengebet.en.aptoide.com/}\linebreak
        \end{flushleft}
    }
    \item {
        \begin{flushleft}
            Server side for "Revengebet". (Python with django)\linebreak
        \end{flushleft}
    }
    \item {
        \begin{flushleft}
            Improved parsing tickets algorithm Novosibirsk water park (\url{http://akvamirnsk.ru}). (Python).\linebreak
        \end{flushleft}
    }
    \item {
        \begin{flushleft}
            Implemented playground for creating urban sites with multi-level admin panel. (\url{https://gorsite.ru/}) (Django with Python)\linebreak
        \end{flushleft}
    }
    \item {
        \begin{flushleft}
            Implemented Siberia Expo web site \url{siberiaexpo.ru}. (Wordpress with php).\linebreak
        \end{flushleft}
    }
\end{cvitems}
}

%------------------------------------------------

\end{cventries}
